---
title: "Analysis of Firms Experiment"
author: "Elea McDonnell Feit"
date: "1/18/2018"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
setwd("/Users/emf75/Google Drive/_Workshops/R for Behavioral Research Workshop/Firms Analysis/")
```

# Data

The data describes an experiment where respondents where given a story about a company that either did or did not take a stand regarding an abortion-related law. Each row describes the story that was given to the repondent and their evaluation of the company. 

- **stand** of a firm with respect to the law was either "against", "for" or "none" (randomly manipulated)  
- **firm.value** was either "results"-oriented or "values"-oriented (randomly manipulated)
- **hypocricy** is a measure of the level of perceived corporate hypocrisy. It is a composite of three perceived hypocrisy scale items.  
- **purchase_int** is the composite score of three purchase intention scale items.  
- **age** is the age of the respondent.  
- **gender** is the gender of the respondent.  

```{r}
d <- read.csv("firms.csv")
d$stand <- as.factor(d$stand)
d$firm.value <- as.factor(d$firm.value)
d$gender <- as.factor(d$gender)
summary(d)
```

# Outliers
After inspecting the data, we realized that observation 30 was incorrectly collected, so we remove them. 
```{r}
d <- d[-30,]
summary(d)
```

# Analysis 

We hypothesize that when values-oriented (versus results-oriented) companies abstain from taking a political stand, consumers perceive them to be hypocritical. This, in turn, will lead to lower purchase intention for the products offered by those companies. Based on this hypothesis, we created a new variable indicating whether the firm was described as taking a stand.
```{r}
d$stand.yn <- as.character(d$stand)
d$stand.yn[d$stand.yn=="against" | d$stand.yn=="for"] <- "stand"
d$stand.yn <- as.factor(d$stand.yn)
summary(d$stand.yn)
```

When value-oriented companies fail to take a stand, they are perceived as hypocritical 

```{r}
boxplot(hypocrisy ~ stand.yn + firm.value, data=d, main="Hypocrisy", ylab="composite hypocrisy score")
```

Statistical significance of the interaction between stand.yn and firm.value is confirmed by ANOVA.

```{r}
m1 <- lm(hypocrisy ~ stand.yn*firm.value, data=d) # interactions
anova(m1)
```

Similarly, purchase intent is lower for those value-oriented firms who do not take a stand.

```{r}
boxplot(purchase_int ~ stand.yn + firm.value, data=d, main="Hypocrisy", ylab="composite hypocrisy score")
```

```{r}
m2 <- lm(purchase_int ~ stand.yn*firm.value, data=d)
anova(m2)
```

I also did some simple t-tests for fun. 
```{r}
t.test(d$hypocrisy[d$stand.yn=="no stand"], d$hypocrisy[d$stand.yn=="stand"])
p1 <- t.test(d$hypocrisy[d$stand.yn=="no stand"], d$hypocrisy[d$stand.yn=="stand"])$p.value
t.test(d$purchase_int[d$stand.yn=="no stand"], d$purchase_int[d$stand.yn=="stand"])
t.test(d$hypocrisy[d$firm.value=="results"], d$hypocrisy[d$firm.value=="values"])
t.test(d$purchase_int[d$firm.value=="results"], d$purchase_int[d$firm.value=="values"])
```
The first test is significant at p= `r p1`. 


# Sample characteristics
The sample contains similar numbers of men and women. 
```{r}
summary(d$gender)
plot(d$gender)
```

The distribution of age is typical for mTurk.
```{r}
summary(d$age)
hist(d$age, main="Histogram of Respondent Age")
```

# Randomization check 
The proportion of women in each of the 6 (= 2 x 3) randomized treatments is similar with one exception. 
```{r}
xtabs(~ gender + stand + firm.value, data=d)
plot(xtabs(~ gender + stand + firm.value, data=d))
```
The distribution of age is similar across the randomly assigned treatments, confirming that the randomization looks okay. 
```{r}
aggregate(age ~ stand + firm.value, data=d, FUN=mean)
plot(aggregate(age ~ stand, data=d, FUN=mean), ylim=c(15,80))
plot(age ~ stand, data=d)
```



