---
title: "Chick Analysis"
author: "Elea McDonnell Feit"
date: "1/18/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Google Drive/_Workshops/R for Behavioral Research Workshop/Chicks Analysis") # change this
```

# Data
```{r}
data <- read.csv("rhea.tables.grams.20150626.csv")
levels(data$treatment) <- c("Control (n=17)\nInvoluntary Bucket", 
                            "Treatment (n=18)\nVoluntary Walk-on")
summary(data)
```

Write a t-test comparing the control and treatment groups. Edit this text to describe the analysis.
```{r}
# to do
```


Conduct an ANOVA on the percent gain as a function of treatment, breading_group, gender and color. 
```{r}
# to do
```

Create a boxplot comparing the control and treatment groups.
```{r}
# to do
```

This is a beanplot (sometimes called violin plot) that was used in the publication. What are the advantages of a beanplot over a boxplot?
```{r}
library(beanplot)
beanplot(pct_gain_10.25~treatment, data=data,
         col=c("lightgray", "black", "black", "red"), 
         ylab="percent", 
         main="Percent Weight Gain Day 10 to Day 25,26") 
abline(h=c(-1:4*100), lty=2, col="dark gray")
```