---
title: "Chick Analysis"
author: "Elea McDonnell Feit"
date: "1/18/2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/repos/RforResearch/Chicks Analysis") # change this
library(tidyverse)
```

# Data
This was data provide to me by Dr. Sue McDonnell on chick growth. This was data from an experiment where....
```{r}
chickdata <- read.csv("rhea.tables.grams.20150626.csv")
#levels(data$treatment) <- c("Control (n=17)\nInvoluntary Bucket", 
#                            "Treatment (n=18)\nVoluntary Walk-on")
summary(chickdata)
glimpse(chickdata)
```

Create a scatterplot showing the relationship between grams at day 0 and grams at day 25. 
```{r}
plot(grams_day25 ~ grams_day0, data=chickdata)

ggplot(data=chickdata, aes(x=grams_day0, y=grams_day25)) + 
  geom_point()
```

A boxplot shows the relationship between a continuous response variable and a discrete or categeorical explanatory variable. An alternative is the beanplot. Mom, this beanplot shows that the data is really noisy and it doesn't look like the hypothized effect is present.  I'm so sorry for your loss. 
```{r}
boxplot(pct_gain_10.25 ~ treatment, data=chickdata)
library(beanplot)
beanplot(pct_gain_10.25 ~ treatment, data=chickdata,
         col=c("lightgray", "black", "black", "red"), 
         ylab="percent", 
         main="Percent Weight Gain Day 10 to Day 25,26")
```

A t-test indicates the difference in percent weight gain is non-significant. 
```{r}
t.test(pct_gain_10.25 ~ treatment, data=chickdata)
```


```{r}
simplemodel <- lm(pct_gain_10.25 ~ (treatment + gender + color + breading_group)^2 , data=chickdata)
summary(simplemodel)
anova(simplemodel)
```

